---
title: "Lab Assignment 3"
output:
  html_document:
    df_print: paged
---
```{r echo=FALSE}
knitr::opts_chunk$set(comment=NA)
```

```{r loadpackages, echo=FALSE, message=FALSE}
# The following packages may be helpful for this assignment
library(dplyr)
library(ggplot2)
library(flextable)
library(tidyr)
```

```{r loaddata, echo=FALSE}
# Load data here
# Change directory if file is not in your working directory
load("insalescall.rdata")
```

# Logistic Regression

The [insalescall.rdata](./insalescall.rdata) file contains a data frame, `insalescall`, which has data on about $3800$ customers of a bank that also sells insurance. The customers in the data were contacted to see if they wanted to buy car insurance with specific levels of coverage. The outcome variable, `buy`, is a factor variable with two levels: *Yes* if they bought and *No* if they did not buy. As these are current customers, the bank has several other variables on each customers:

* `age`: age of the customer
* `balance`: average bank balance over the past $12$ months
* `carloan`: factor variable with two levels (*Yes* if the customer has a car loan through the bank, *No* otherwise)
* `educ`: factor variable with three levels indicating education level (*LT_HS* for less than high school, *HS* for high school, *GT_HS* for some college and above)
* `marital`: factor variable with three levels indicating marital status (*Divorced*, *Married*, *Single*)
* `homeins`: factor variable with two levels (*Yes* if the customer has homeowner's insurance through the bank, *No* otherwise)
* `preout`: factor variable with three levels indicating the result of a previous, non-car insurance sales call (*No previous*, *Failure*, *Success*)

The goal is to determine what customer characteristics can be used to predict the likelihood of purchase.  To begin, get a feel for some of the variables by answering the following questions.  Include any output used to answer the questions.

Use this [LA03WriteUp.Rmd](./LA03WriteUp.Rmd) file to answer the questions below.  If a question requires code, put the code in the code chunk (under **Code**). When complete, Knit the file to PDF, save that file and submit the PDF file to Canvas.  

**NOTE**: If using BGSU's Virtual Computing Lab, you cannot Knit to PDF.  In that situation, download the ".Rmd" file and submit that to Canvas.

---

## Question 1

**Question** *(4 points)*  
Using summary statistics, answer the following questions:

a. What percent of customers purchased car insurance?
b. How does the average age and balance compare for those that purchased and those that did not purchase? Do you think these variables will drive the purchase of car insurance?


[R Tutorial](https://jdmeyer73.github.io/MKT4320RTut/examining-and-summarizing-data.html#tables-and-statistics){target="_blank" rel="noopener"}

---

## Question 2

**Question** *(4 points)*  
Create stacked bar charts to visualize how education level might affect the purchase of car insurance.  What percent of college graduates purchased college insurance? Create a second stacked bar chart for marital status and the purchase of car insurance. How does being married compare with the other two categories in terms of buying car insurance?


[R Tutorial](https://jdmeyer73.github.io/MKT4320RTut/examining-and-summarizing-data.html#stacked-bar-chart){target="_blank" rel="noopener"}

---

## Question 3

**Question** *(3 points)*  
In preparation for running a logistic regression, create training ($75\%$) and test/holdout ($25\%$) samples. Use a `set.seed(4320)` so that everyone produces the same samples. Report how many observations each sample has and the number of observations that bought car insurance.

[R Tutorial](https://jdmeyer73.github.io/MKT4320RTut/logistic-regression-binary.html#creating-train-and-test-samples){target="_blank" rel="noopener"}

---

## Question 4

**Question** *(6 points)*  
Run a logistic regression on the training sample only, using `age`, `balance`, `homeins`, `carloan`, `preout`, and `educ` as the predictors of the dependent variable `buy`.  Discuss the overall model fit on the training sample, including McFadden's pseudo-$R^2$, the classification matrix, and the ROC curve. You will need the following user-defined functions:

* [logreg_cm](./logreg_cm.R) produces the Classification Matrix
* [logreg_roc](./logreg_roc.R) produces the ROC Curves

[R Tutorial for running model](https://jdmeyer73.github.io/MKT4320RTut/logistic-regression-binary.html#logistic-regression-using-glm){target="_blank" rel="noopener"}  
[R Tutorial for classification matrix](https://jdmeyer73.github.io/MKT4320RTut/logistic-regression-binary.html#classification-matrix){target="_blank" rel="noopener"}  
[R Tutorial for ROC curve](https://jdmeyer73.github.io/MKT4320RTut/logistic-regression-binary.html#roc-curve){target="_blank" rel="noopener"}

---

## Question 5

**Question** *(5 points)*  
Discuss the overall model fit on the holdout sample using the classification matrix and ROC curve.

---

## Question 6

**Question** *(4 points)*  
Use the user-defined function [or_table](./or_table.R) to produce a table with odds-ratio coefficients.  Which continuous variables significantly increase the odds of the customer purchasing car insurance? Interpret any that are significant.

[R Tutorial](https://jdmeyer73.github.io/MKT4320RTut/logistic-regression-binary.html#logistic-regression-using-glm){target="_blank" rel="noopener"}

---

## Question 7

**Question** *(10 points)*  
Which levels of the factor/categorical variables significantly increase the odds of the customer purchasing car insurance?  Interpret each of these (be sure to reference the base category).

---

## Question 8

**Question** *(6 points)*  
Use the user-defined function [gainlift](./gainlift.R) to produce gain and lift plots and tables. If we were to contact the top 20% of predicted buyers in the holdout sample, what percent of all buyers would we get?  What is our lift when contacting the top 20%. Interpret each number.

[R Tutorial](https://jdmeyer73.github.io/MKT4320RTut/logistic-regression-binary.html#gainlift-charts-and-tables){target="_blank" rel="noopener"}

---

## Question 9

**Question** *(3 points)*  
Suppose the goal is to reach 50% of those in the holdout sample that would actually buy.  Approximately what proportion of customers (ranked in order of likelihood to buy) would we need to contact?

---

## Question 10

**Question** *(15 points)*  
Suppose you are a marketing consultant for this bank.  What marketing advice do you have for the brand’s marketing team?  Using bullet points, provide two or three carefully thought out suggestions.